Efficient static analysis of Marlowe contracts

### 2020-05-22 papers/static_analysis2020/paper.tex
Improve explanation of transaction and segment mapping

On the other hand, if the minimum slot number of a transaction is greater
or equal than the slot number in the timeout, then the first transaction
will execute past the \texttt{When} and into the timeout branch, and
we will not need the second transaction. In the same way, if we include
an input that is allowed by the \texttt{When} into the first transaction,
then the first transaction will continue into the corresponding \texttt{When}
branch, and we will not need the second transaction.

We cannot just constrain the maximum slot number of the first transaction
to be less than the timeout in the \texttt{When} because, if we do
that, then we will miss executions where one transaction expires several
\texttt{When} in a row, or where it expires one \texttt{When} and provides
the right input for later \texttt{When}. And we cannot not constrain
the maximum slot number of the first transaction because then we will
not know whether the first transaction goes beyond the \texttt{When}
or not.

>>>>

On the other hand, this segmentation is not general enough, because there is
an edge case. A transaction may execute past a \texttt{When} if the minimum
slot number in the transaction is greater or equal than the timeout of the
\texttt{When}. If the transaction expires the \texttt{When} we can no longer
separate the execution before the \texttt{When} and after the \texttt{When}
into two different transactions, because we know that the timeout branch of the
\texttt{When} will be executed as part of the first transaction, and thus
it will use the slot interval of the first
transaction (same used for the first segment).

This is not only true for the timeout branch, if we include
an input that is allowed by the \texttt{When} into the first transaction,
then the first transaction will continue into the corresponding \texttt{When}
branch, and we will not use a second transaction.

We cannot just constrain the maximum slot number of the first transaction
to be less than the timeout in the \texttt{When} because, if we do
that, then we will miss executions where one transaction expires several
\texttt{When} in a row, or where it expires one \texttt{When} and provides
the right input for later \texttt{When}. And we cannot just not constrain
the maximum slot number of the first transaction because then we will
not know to which segments each transaction applies.
